\section{skelsurf.c File Reference}
\label{skelsurf_8c}\index{skelsurf.c@{skelsurf.c}}
surfacic binary skeleton guided by a priority image  




\label{_details}
\subsection{Detailed Description}
surfacic binary skeleton guided by a priority image 

{\bf Usage:} skelsurf in.pgm prio connex [inhibit] out.pgm

{\bf Description:} Surfacic binary skeleton guided by a priority image. The lowest values of the priority image correspond to the highest priority.

The parameter {\bf prio} is either an image (byte or int32\_\-t), or a numerical code indicating that a distance map will be used as a priority image; the possible choices are: \begin{itemize}
\item 0: approximate euclidean distance \item 1: approximate quadratic euclidean distance \item 2: chamfer distance \item 3: exact quadratic euclidean distance \item 6: 6-distance in 3d \item 18: 18-distance in 3d \item 26: 26-distance in 3d\end{itemize}
The parameter {\bf connex} indicates the connectivity of the binary object. Possible choices are 6, 26.

If the parameter {\bf inhibit} is given and is a binary image name, then the points of this image will be left unchanged.

Let X be the set corresponding to the input image {\bf in.pgm}. Let P be the function corresponding to the priority image. Let I be the set corresponding to the inhibit image, if given, or the empty set otherwise. The algorithm is the following:



\begin{footnotesize}\begin{verbatim}
C = {y in F | Tb(y) > 1}
Repeat until stability
  choose a point x in X, simple for X, such that C[x] == 0 
    and such that P[x] is minimal
  X = X \ {x}
  for all y in gamma(x)
    if Tb(y) > 1 then C[y] = 1
Result: X
\end{verbatim}
\end{footnotesize}


where Tb(y) refers to the second connectivity number of y, that is, (informally) the number of connected components of gamma(y) inter complement(X).

References:\par
 [BC07] G. Bertrand and M. Couprie: {\tt \char`\"{}Transformations topologiques discretes\char`\"{}}, in {\em G\'{e}om\'{e}trie discr\`{e}te et images num\'{e}riques\/}, D. Coeurjolly and A. Montanvert and J.M. Chassery, pp.~187-209, Herm\`{e}s, 2007.\par


{\bf Types supported:} byte 3d

{\bf Category:} topobin

\begin{Desc}
\item[Author:]Michel Couprie \end{Desc}
